Supplementary figures

### 2021-07-02 code/supplemental_v2.Rmd
Update stanfit for all models in s5 fig

load("../data/deadpat_all.rda")
deadpat <- deadpat %>% rownames_to_column(var = "stanid")
## convert negative tdeath to 0
deadpat[which(deadpat$tevent < 0), "tevent"] <- 0
model <- c("knn", "icluster", "coca", "tis")
tdeath.error <- list() ## store error values
entropy <- list() 
for(n in model) {
  ## Load correct model
  if(n == "knn") {
    load("./survival/survmodel_effcl_knn_062821.stansave")
  } else if(n == "icluster") {
    load("./survival/survmodel_effcl_icluster_062821.stansave")
  } else if (n == "coca") {
    load("./survival/survmodel_effcl_coca_062821.stansave")
  } else if (n == "tis") {
    load("./survival/survmodel_effcl_tis_062821.stansave")
  } else {
    print("Model does not exist")
  }
  ## Extract tdeath for "adeath" indivduals
  tdeath <- samps %>% as.data.frame(.) %>% .[, grep(pattern = "tdeath", x = names(.))]
  names(tdeath) <- gsub("tdeath\\[(.*)\\]","\\1", names(tdeath)) ## update colname with stanid
  tdeath <- tdeath %>% gather(data = ., key = "stanid", value = "predicted") %>%
    left_join(x = ., y = deadpat[,c("stanid", "tevent", "eventtype")], by = "stanid") %>%
    dplyr::filter(eventtype == "adeath")
  ## Calculate error for each sample
  tdeath$error <- tdeath$predicted - tdeath$tevent
  tdeath.error[[n]] <- tdeath$error
  ## Split error data into bins and tally up 
  tdeath <- tdeath %>% mutate(ebin = cut(x = error,
                                         breaks = evaluebreak,
                                         right = T,
                                         labels = elabel))
  eprob <- as.data.frame(table(tdeath$ebin))
  eprob <- eprob %>% dplyr::filter(Freq > 0) %>%
    mutate(prob = Freq / nrow(tdeath))
  ## Entropy calculation
  entropy[[n]] <- round(-sum(eprob$prob*log(eprob$prob))/log(2), digit = 3)
}
knn <- data.frame(error = tdeath.error$knn,
                  model = "knn")
icluster <- data.frame(error = tdeath.error$icluster,
                       model = "icluster")
coca <- data.frame(error = tdeath.error$coca,
                   model = "coca")
tis <- data.frame(error = tdeath.error$tis,
                   model = "tis")
tdeath.error <- rbind(knn, icluster, coca, tis); rm(knn, icluster, coca, tis); gc()

@@

for(n in model) {
   ## Load correct model
  if(n == "knn") {
    load("./survival/survmodel_effcl_knn_062821.stansave")
  } else if(n == "icluster") {
    load("./survival/survmodel_effcl_icluster_062821.stansave")
  } else if (n == "coca") {
    load("./survival/survmodel_effcl_coca_062821.stansave")
  } else if (n == "tis") {
    load("./survival/survmodel_effcl_tis_062821.stansave")
  }
  else {
    print("Model does not exist")
  }
  dfs <- as.data.frame(samps) %>% 
    select(starts_with("tdeath[")) %>%
    stack(.) %>%
    'colnames<-' (c("tdeath", "stanid")) %>%
    .[sample(x = nrow(.), size = 1e5),]
  assign(x = n, value = dfs)
}

@@

s5.2 <- ggplot(data = tdeath.error, aes(x = error, group = model, fill = model)) +
  geom_density(alpha = 0.5) +
  theme_minimal() +
  scale_x_continuous(breaks=seq(-4000, 4000, by = 2000), limits = c(-3650,3650)) +
  labs(x = "Error (Predicted - Actual)", y = "Density")#, 
       #subtitle = paste0("Entropy - knn: ", entropy$knn, " ; icluster: ", entropy$icluster, "\ncoca: ", entropy$coca, " ; tis: ", entropy$tis))

>>>>

load("../data/deadpat_all.rda")
deadpat <- deadpat %>% rownames_to_column(var = "stanid")
## convert negative tdeath to 0
deadpat[which(deadpat$tevent < 0), "tevent"] <- 0
model <- c("knn", "icluster", "coca", "tis")
tdeath.error <- list() ## store error values
entropy <- list() 
for(n in model) {
  ## Load correct model
  if(n == "knn") {
    load("./survival/survmodel_effcl_knn_070121.stansave")
  } else if(n == "icluster") {
    load("./survival/survmodel_effcl_icluster_070121.stansave")
  } else if (n == "coca") {
    load("./survival/survmodel_effcl_coca_070121.stansave")
  } else if (n == "tis") {
    load("./survival/survmodel_effcl_tis_070121.stansave")
  } else {
    print("Model does not exist")
  }
  ## Extract tdeath for "adeath" indivduals
  tdeath <- samps %>% as.data.frame(.) %>% .[, grep(pattern = "tdeath", x = names(.))]
  names(tdeath) <- gsub("tdeath\\[(.*)\\]","\\1", names(tdeath)) ## update colname with stanid
  tdeath <- tdeath %>% gather(data = ., key = "stanid", value = "predicted") %>%
    left_join(x = ., y = deadpat[,c("stanid", "tevent", "eventtype")], by = "stanid") %>%
    dplyr::filter(eventtype == "adeath")
  ## Calculate error for each sample
  tdeath$error <- tdeath$predicted - tdeath$tevent
  tdeath.error[[n]] <- tdeath$error
  ## Split error data into bins and tally up 
  tdeath <- tdeath %>% mutate(ebin = cut(x = error,
                                         breaks = evaluebreak,
                                         right = T,
                                         labels = elabel))
  eprob <- as.data.frame(table(tdeath$ebin))
  eprob <- eprob %>% dplyr::filter(Freq > 0) %>%
    mutate(prob = Freq / nrow(tdeath))
  ## Entropy calculation
  entropy[[n]] <- round(-sum(eprob$prob*log(eprob$prob))/log(2), digit = 3)
}
knn <- data.frame(error = tdeath.error$knn,
                  model = "knn")
icluster <- data.frame(error = tdeath.error$icluster,
                       model = "icluster")
coca <- data.frame(error = tdeath.error$coca,
                   model = "coca")
tis <- data.frame(error = tdeath.error$tis,
                   model = "tis")
tdeath.error <- rbind(knn, icluster, coca, tis); rm(knn, icluster, coca, tis); gc()

@@

for(n in model) {
   ## Load correct model
  if(n == "knn") {
    load("./survival/survmodel_effcl_knn_070121.stansave")
  } else if(n == "icluster") {
    load("./survival/survmodel_effcl_icluster_070121.stansave")
  } else if (n == "coca") {
    load("./survival/survmodel_effcl_coca_070121.stansave")
  } else if (n == "tis") {
    load("./survival/survmodel_effcl_tis_070121.stansave")
  }
  else {
    print("Model does not exist")
  }
  dfs <- as.data.frame(samps) %>% 
    select(starts_with("tdeath[")) %>%
    stack(.) %>%
    'colnames<-' (c("tdeath", "stanid")) %>%
    .[sample(x = nrow(.), size = 1e5),]
  assign(x = n, value = dfs)
}

@@

s5.2 <- ggplot(data = tdeath.error, aes(x = error, group = model, fill = model)) +
  geom_density(alpha = 0.5) +
  theme_minimal() +
  #scale_x_continuous(breaks=seq(-4000, 4000, by = 2000), limits = c(-3650,3650)) +
  labs(x = "Error (Predicted - Actual)", y = "Density")#, 
       #subtitle = paste0("Entropy - knn: ", entropy$knn, " ; icluster: ", entropy$icluster, "\ncoca: ", entropy$coca, " ; tis: ", entropy$tis))
